Adopting agile software development in the large organizations: A systematic literature review

### 2014-08-10 journal/content.tex
Bibliography settings
Changed section labels for thesis style

\section{Introduction}

@@

\section{Background}
\label{sec:background}

\subsection{Agile software development}

@@

\subsection{Large scale agile development}

@@

\subsection{Adopting agile methods in large organizations}

@@

% \subsection{Challenges in adopting agile methods}
%

% \subsection{Success factors in adopting agile methods}
%

\subsection{Summary of things that may need to be explained}

@@

\section{Research method}
\label{sec:method}

@@

\subsection{Research questions}

@@

\subsection{Definition of large scale}
\label{sec:largescale}

@@

\subsection{Research process}

@@

\subsubsection{Inclusion criteria}
\label{sec:inclusioncriteria}

@@

\subsubsection{Preliminary searches}

@@

\subsubsection{Identification of primary studies}

@@

\subsubsection{Study selection}

@@

\subsubsection{Handling of duplicate reports on a single case}

@@

\subsubsection{Study quality assessment}

@@

\subsubsection{Coding of primary studies}
\label{sec:coding}

@@

\subsubsection{Validation of coding}

@@

\subsubsection{Synthesis of primary studies based on coding}

@@

\subsection{Threats to validity and limitations}

@@

\section{Results}
\label{sec:results}

@@

\subsection{Overview of primary studies}

@@

\subsection{Agile methods used}

@@

\subsection{Reasons to change}

@@

\subsubsection{Business demands speed and flexibility}

@@

\subsubsection{Management issues}

@@

\subsubsection{Process problems}

@@

\subsubsection{Other reasons to change}

@@

\subsection{Transformation process}

@@

\subsubsection{The initial state of the organization}

@@

\subsubsection{Modes of transformation}

@@

\subsubsection{How change was lead}

@@

\subsubsection{Training, coaching, and awareness}

@@

\subsubsection{Piloting}

@@

\subsubsection{Investing in new structures in transformation}

@@

\subsection{Challenges in transformation}

@@

\subsubsection{Change resistance}

@@

\subsubsection{Lack of investment in transformation}

@@

\subsubsection{Agile is difficult to implement}

@@

\subsubsection{Coordinating work between many teams}

@@

\subsubsection{Issues specific to large organizations}

@@

\subsubsection{Integrating requirements management and quality assurance}

@@

\subsubsection{Integrating other functions than development to agile}

@@

\subsubsection{Other challenges in transformation}

@@

\subsection{Success factors in transformation}

@@

\subsubsection{Management support}

@@

\subsubsection{Commitment to change}

@@

\subsubsection{Leadership and alignment}

@@

\subsubsection{Use of piloting}

@@

\subsubsection{Choosing the agile model to fit the organization}

@@

\subsubsection{Considering the Product Owner role and requirements management}

@@

\subsubsection{Training and coaching}

@@

\subsubsection{Communication and transparency in the change}

@@

\subsubsection{Enable autonomy for development teams}

@@

\subsubsection{Choosing the right people}

@@

\subsubsection{Other success factors}

@@

\section{Discussion}
\label{sec:discussion}

@@

% ---------------------------------------------------------------------
\section{Limitations and future research}
\label{sec:conclusion}

@@

\bibliographystyle{elsarticle-harv}
%\bibliographystylegen{plain}

>>>>

\chapter{Introduction}

@@

\chapter{Background}
\label{sec:background}

\section{Agile software development}

@@

\section{Large scale agile development}

@@

\section{Adopting agile methods in large organizations}

@@

% \section{Challenges in adopting agile methods}
%

% \section{Success factors in adopting agile methods}
%

\section{Summary of things that may need to be explained}

@@

\chapter{Research method}
\label{sec:method}

@@

\section{Research questions}

@@

\section{Definition of large scale}
\label{sec:largescale}

@@

\section{Research process}

@@

\subsection{Inclusion criteria}
\label{sec:inclusioncriteria}

@@

\subsection{Preliminary searches}

@@

\subsection{Identification of primary studies}

@@

\subsection{Study selection}

@@

\subsection{Handling of duplicate reports on a single case}

@@

\subsection{Study quality assessment}

@@

\subsection{Coding of primary studies}
\label{sec:coding}

@@

\subsection{Validation of coding}

@@

\subsection{Synthesis of primary studies based on coding}

@@

\section{Threats to validity and limitations}

@@

\chapter{Results}
\label{sec:results}

@@

\section{Overview of primary studies}

@@

\section{Agile methods used}

@@

\section{Reasons to change}

@@

\subsection{Business demands speed and flexibility}

@@

\subsection{Management issues}

@@

\subsection{Process problems}

@@

\subsection{Other reasons to change}

@@

\section{Transformation process}

@@

\subsection{The initial state of the organization}

@@

\subsection{Modes of transformation}

@@

\subsection{How change was lead}

@@

\subsection{Training, coaching, and awareness}

@@

\subsection{Piloting}

@@

\subsection{Investing in new structures in transformation}

@@

\section{Challenges in transformation}

@@

\subsection{Change resistance}

@@

\subsection{Lack of investment in transformation}

@@

\subsection{Agile is difficult to implement}

@@

\subsection{Coordinating work between many teams}

@@

\subsection{Issues specific to large organizations}

@@

\subsection{Integrating requirements management and quality assurance}

@@

\subsection{Integrating other functions than development to agile}

@@

\subsection{Other challenges in transformation}

@@

\section{Success factors in transformation}

@@

\subsection{Management support}

@@

\subsection{Commitment to change}

@@

\subsection{Leadership and alignment}

@@

\subsection{Use of piloting}

@@

\subsection{Choosing the agile model to fit the organization}

@@

\subsection{Considering the Product Owner role and requirements management}

@@

\subsection{Training and coaching}

@@

\subsection{Communication and transparency in the change}

@@

\subsection{Enable autonomy for development teams}

@@

\subsection{Choosing the right people}

@@

\subsection{Other success factors}

@@

\chapter{Discussion}
\label{sec:discussion}

@@

% ---------------------------------------------------------------------
\chapter{Limitations and future research}
\label{sec:conclusion}

@@
